\documentclass{scspaperproc}

\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage{ulem}

% To do: here's how Stephen compiles the paper from the ANNSIM directory:
% pdflatex scs23paper.tex 
% bibtex scs23paper
% pdflatex scs23paper.tex
% pdflatex scs23paper.tex
%
% By putting this into an alias in my .bashrc with:
% alias lt="pdflatex scs23paper.tex ; bibtex scs23paper ; pdflatex % scs23paper.tex ; pdflatex scs23paper.tex"
% I can compile the paper to a PDF in one shot.
%
% When adding new papers to Zotero, be sure to put them in the ANNSIM folder
% (or subfolder), then highlight all and Export... to BibTex mode, saving the
% file under the name bib.bib (in assets subdirectory). Don't forget to commit
% your changes to bib.bib as well as your changes to any of the .text files!


\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black,bookmarks=false]{hyperref}

% Avoid overrunning the right margin; you are welcome to remove this, provided that you take care not to overrun the right margin anywhere in your paper
\sloppy

\begin{document}

\SCSpagesetup{Davies and Peura}

\def\SCSconferencename{Annual Simulation Conference}

\def\SCSconferenceacro{ANNSIM'24}

\def\SCSpublicationyear{2024}

\def\SCSconferenceeditors{P.J. Giabbanelli, I. David, C. Ruiz-Martin, B. Oakes and R. C\'{a}rdenas}

\def\SCSconferencedates{May 20-23}

\def\SCSconferencevenue{American University, DC, USA}

\title{THE INTERACTION BETWEEN HETEROGENEOUS VOTING STRATEGIES AND DYNAMIC
VOTE-SEEKING CAMPAIGNS: AN AGENT-BASED MODEL}

\textit{(Author names/affiliations to be redacted for initial blind submission.)}
\author[\authorrefmark{1}]{\sout{Stephen Davies}}
\author[\authorrefmark{1}]{\sout{Harmony Peura}}

\affil[\authorrefmark{1}]{\sout{University of Mary Washington Computer Science,
Virginia USA}}
\affil[ ]{\textit {\sout{stephen@umw.edu}}}
\affil[ ]{\textit {\sout{hpeura@umw.edu}}}


\maketitle

\section*{Abstract}

Political candidates in a democracy articulate positions on the issues of the
day, but they are also highly aware of voter sentiment on those issues, and
tailor their campaigns accordingly as they seek to win elections. Voters, too,
adjust their political opinions based on (among other things) interactions with
others in their social network. We present an agent-based simulation that
models this dynamic interplay between candidates and voters, in order to shed
light on what outcomes candidates can expect to result from a policy of
``chasing'' votes. The voters in our simulation differ from one another in the
decision procedure they use in choosing who to vote for -- these voting
algorithms are modeled on results from the political science literature about
the different ways voters make decisions. Our model can thus be used to
experiment with a virtual electorate, to determine the conditions under which
vote-chasing candidates gain an advantage or perhaps even cause the election
outcome to be objectively irrational.


\textbf{Keywords:} opinion dynamics, ABM, election, voting

\input{intro.tex}
\input{related.tex}
\input{model.tex}
\input{experimentation.tex}
\input{results.tex}
\input{discussion.tex}
\input{future.tex}
\input{conclusions.tex}


\bibliographystyle{scsproc}

\bibliography{assets/bib}



\section*{Author Biographies}

\textit{(To be redacted for initial blind submission.)}

\sout{\textbf{\uppercase{Stephen Davies}} is an international spy, sought-after
public speaker, and former member of the Jedi Council on Coruscant. He's
considered armed and dangerous and should be approached with caution.
His email address is \email{stephen@umw.edu}.}

\sout{\textbf{\uppercase{Harmony Peura}} is an Honors student in the University of
Mary Washington Computer Science department, and also sings alto for several
acapella groups. She has climbed Mt.~Everest on three separate occasions. Her
email address is \email{hpeura@umw.edu}.}


\end{document}
